EWJN from a BCS Superconductor

### 2021-02-26 paper.tex
Adds figures to text

>>>>

\section{Additional Figures}

Slices of \cref{fig:Cliff} are plotted for different frequencies in \crefrange{fig:omega:5}{fig:omega:85}, to better show the behaviour of the cliff-edge.
Additionally, we have plotted different values of the impurity collision frequency $\tau$, to show how dirtier superconductors, with smaller $\tau$, have much higher values for the noise.

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/5.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:5}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/15.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:15}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/25.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:25}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/35.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:35}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/45.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:45}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/55.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:55}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/65.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:65}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/75.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:75}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constOmega/85.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $\omega$.} \label{fig:omega:85}
\end{figure}

Similarly, we can make slices of \cref{fig:Cliff} for constant temperature, and show how the noise drops off for a different frequency.
These slices are plotted in \crefrange{fig:T:10}{fig:T:40}.

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constT/10.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:10}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constT/20.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:20}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constT/30.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:30}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{constT/40.jpg}
	\caption{A slice of \cref{fig:Cliff} for constant $T$.} \label{fig:T:40}
\end{figure}
